---
title: "data_wrangle"
author: "Cheryl Logan"
date: "4/10/2018"
output: html_document
---

Read in the measurements for gill filament width (n=3), lamellar length (n=3) and lamellar width (n=3 for 3 different lamellae) for 31 excel files. Measurements were made using ImageJ in triplicate

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
library(tidyverse) # load tidverse package
```

## Load Dataset
Open the data files using tidyverse `read_csv` function

# to load as .csv
cross355 <- read_csv("/Users/loga8761/Google Drive/LoganLab/People/Devon/Results KGB 355 cross 2017-09-01.csv")

control_370_1 <- read_csv("/Users/loga8761/Google Drive/LoganLab/People/Devon/Results KGB 370 control 2017-07-10.csv")

control_370_2 <- read_csv("/Users/loga8761/Google Drive/LoganLab/People/Devon/results KGB 370 control 2 2017-07-10.csv")

control_371 <- read.csv("C:/Users/Dprey/Desktop/gill results/control_371")
```{r load data, message = FALSE, warning = FALSE}


cross_355 <- read_csv("C:/Users/Dprey/Desktop/gill results/cross_355.csv")

control_370 <- read_csv("C:/Users/Dprey/Desktop/gill results/control_370.csv")

control_370_2 <- read_csv("C:/Users/Dprey/Desktop/gill results/control_370_2.csv")

control_371 <- read_csv("C:/Users/Dprey/Desktop/gill results/control_371.csv")

control_372 <- read_csv("C:/Users/Dprey/Desktop/gill results/control_372.csv")

control_373 <- read_csv("C:/Users/Dprey/Desktop/gill results/control_373.csv")

control_374 <- read_csv("C:/Users/Dprey/Desktop/gill results/control_374.csv")

control_375 <- read_csv("C:/Users/Dprey/Desktop/gill results/control_375.csv")

control_376 <- read_csv("C:/Users/Dprey/Desktop/gill results/control_376.csv")

control_378 <- read_csv("C:/Users/Dprey/Desktop/gill results/control_378.csv")

control_379 <- read_csv("C:/Users/Dprey/Desktop/gill results/control_379.csv")

unknown_382 <- read_csv("C:/Users/Dprey/Desktop/gill results/unknown_382.csv")

PH_385 <- read_csv("C:/Users/Dprey/Desktop/gill results/PH_385.csv")

PH_394 <- read_csv("C:/Users/Dprey/Desktop/gill results/PH_394.csv")

PH_395 <- read_csv("C:/Users/Dprey/Desktop/gill results/PH_395.csv")

PH_400 <- read_csv("C:/Users/Dprey/Desktop/gill results/PH_400.csv")

DO_401 <- read_csv("C:/Users/Dprey/Desktop/gill results/DO_401.csv")

DO_406 <- read_csv("C:/Users/Dprey/Desktop/gill results/DO_406.csv")

DO_409 <- read_csv("C:/Users/Dprey/Desktop/gill results/DO_409.csv")

DO_413 <- read_csv("C:/Users/Dprey/Desktop/gill results/DO_413.csv")

DO_420 <- read_csv("C:/Users/Dprey/Desktop/gill results/DO_420.csv")

cross_432 <- read_csv("C:/Users/Dprey/Desktop/gill results/cross_432.csv")

cross_434 <- read_csv("C:/Users/Dprey/Desktop/gill results/cross_434.csv")

cross_434_2 <- read_csv("C:/Users/Dprey/Desktop/gill results/cross_434_2.csv")

cross_437 <- read_csv("C:/Users/Dprey/Desktop/gill results/cross_437.csv")

cross_438_1 <- read_csv("C:/Users/Dprey/Desktop/gill results/cross_438_1.csv")

cross_438_2 <- read_csv("C:/Users/Dprey/Desktop/gill results/cross_438_2.csv")

cross_438_3 <- read_csv("C:/Users/Dprey/Desktop/gill results/cross_438_3.csv")

DO_491 <- read_csv("C:/Users/Dprey/Desktop/gill results/DO_491.csv")

PH_554 <- read_csv("C:/Users/Dprey/Desktop/gill results/PH_554.csv")

DO_413 <- read_csv("C:/Users/Dprey/Desktop/gill results/DO_413.csv")

# Devon- keep writing the code to load all of your files! This is fun
```