---
title: "data_wrangle"
author: "Cheryl Logan"
date: "4/10/2018"
output: html_document
---

Read in the measurements for gill filament width (n=3), lamellar length (n=3) and lamellar width (n=3 for 3 different lamellae) for 31 excel files. Measurements were made using ImageJ in triplicate

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
library(tidyverse) # load tidverse package
```

## Load Dataset
Open the data files using tidyverse `read_csv` function

# to load as .csv
cross355 <- read_csv("/Users/loga8761/Google Drive/LoganLab/People/Devon/Results KGB 355 cross 2017-09-01.csv")

control_370_1 <- read_csv("/Users/loga8761/Google Drive/LoganLab/People/Devon/Results KGB 370 control 2017-07-10.csv")

control_370_2 <- read_csv("/Users/loga8761/Google Drive/LoganLab/People/Devon/results KGB 370 control 2 2017-07-10.csv")

control_371 <- read.csv("C:/Users/Dprey/Desktop/gill results/control_371")
```{r load data, message = FALSE, warning = FALSE}


cross_355 <- read_csv("C:/Users/Dprey/Desktop/gill results/cross_355.csv")
cross_355 <-  mutate(cross_355, ID="355", treatment="cross")
  
#control_370 <- read_csv("C:/Users/Dprey/Desktop/gill results/control_370.csv")
#control_370 <-  mutate(control_370, ID="370", treatment="control")

control_370_2 <- read_csv("C:/Users/Dprey/Desktop/gill results/control_370_2.csv")
control_370_2 <-  mutate(control_370_2, ID="370_2", treatment="control")

control_371 <- read_csv("C:/Users/Dprey/Desktop/gill results/control_371.csv")
control_371 <-  mutate(control_371, ID="371", treatment="control")

control_372 <- read_csv("C:/Users/Dprey/Desktop/gill results/control_372.csv")
control_372 <-  mutate(control_372, ID="372", treatment="control")

control_373 <- read_csv("C:/Users/Dprey/Desktop/gill results/control_373.csv")
control_373 <-  mutate(control_373, ID="373", treatment="control")

control_374 <- read_csv("C:/Users/Dprey/Desktop/gill results/control_374.csv")
control_374 <-  mutate(control_374, ID="374", treatment="control")

control_375 <- read_csv("C:/Users/Dprey/Desktop/gill results/control_375.csv")
control_375 <-  mutate(control_375, ID="375", treatment="control")

control_376 <- read_csv("C:/Users/Dprey/Desktop/gill results/control_376.csv")
control_376 <-  mutate(control_376, ID="376", treatment="control")

control_378 <- read_csv("C:/Users/Dprey/Desktop/gill results/control_378.csv")
control_378 <-  mutate(control_378, ID="378", treatment="control")

control_379 <- read_csv("C:/Users/Dprey/Desktop/gill results/control_379.csv")
control_379 <-  mutate(control_379, ID="379", treatment="control")

#unknown_382 <- read_csv("C:/Users/Dprey/Desktop/gill results/unknown_382.csv")
#unknown_382 <-  mutate(unknown_382, ID="382", treatment="unknown")

PH_385 <- read_csv("C:/Users/Dprey/Desktop/gill results/PH_385.csv")
PH_385 <-  mutate(PH_385, ID="385", treatment="PH")

PH_394 <- read_csv("C:/Users/Dprey/Desktop/gill results/PH_394.csv")
PH_394 <-  mutate(PH_394, ID="394", treatment="PH")

PH_395 <- read_csv("C:/Users/Dprey/Desktop/gill results/PH_395.csv")
PH_395 <-  mutate(PH_395, ID="395", treatment="PH")

PH_400 <- read_csv("C:/Users/Dprey/Desktop/gill results/PH_400.csv")
PH_400 <-  mutate(PH_400, ID="400", treatment="PH")

DO_401 <- read_csv("C:/Users/Dprey/Desktop/gill results/DO_401.csv")
DO_401 <-  mutate(DO_401, ID="401", treatment="DO")

DO_406 <- read_csv("C:/Users/Dprey/Desktop/gill results/DO_406.csv")
DO_406 <-  mutate(DO_406, ID="406", treatment="DO")

DO_409 <- read_csv("C:/Users/Dprey/Desktop/gill results/DO_409.csv")
DO_409 <-  mutate(DO_409, ID="409", treatment="DO")

DO_413 <- read_csv("C:/Users/Dprey/Desktop/gill results/DO_413.csv")
DO_413 <-  mutate(DO_413, ID="413", treatment="DO")

DO_420 <- read_csv("C:/Users/Dprey/Desktop/gill results/DO_420.csv")
DO_420 <-  mutate(DO_420, ID="420", treatment="DO")

cross_432 <- read_csv("C:/Users/Dprey/Desktop/gill results/cross_432.csv")
cross_432 <-  mutate(cross_432, ID="432", treatment="cross")

#cross_434 <- read_csv("C:/Users/Dprey/Desktop/gill results/cross_434.csv")
#cross_434 <-  mutate(cross_434, ID="434", treatment="cross")

cross_434_2 <- read_csv("C:/Users/Dprey/Desktop/gill results/cross_434_2.csv")
cross_434_2 <-  mutate(cross_434_2, ID="434_2", treatment="cross")

cross_437 <- read_csv("C:/Users/Dprey/Desktop/gill results/cross_437.csv")
cross_437 <-  mutate(cross_437, ID="437", treatment="cross")

cross_438_1 <- read_csv("C:/Users/Dprey/Desktop/gill results/cross_438_1.csv")
cross_438_1 <-  mutate(cross_438_1, ID="438", treatment="cross")

#cross_438_2 <- read_csv("C:/Users/Dprey/Desktop/gill results/cross_438_2.csv")
#cross_438_2 <-  mutate(cross_438_2, ID="438_2", treatment="cross")

#cross_438_3 <- read_csv("C:/Users/Dprey/Desktop/gill results/cross_438_3.csv")
#cross_438_3 <-  mutate(cross_438_3, ID="438_3", treatment="cross")


DO_491 <- read_csv("C:/Users/Dprey/Desktop/gill results/DO_491.csv")
DO_491 <-  mutate(DO_491, ID="491", treatment="DO")


PH_554 <- read_csv("C:/Users/Dprey/Desktop/gill results/PH_554.csv")
PH_554 <-  mutate(PH_554, ID="554", treatment="PH")



# Devon- keep writing the code to load all of your files! This is fun
```
bind all data sets together into single data frame

Repeat measurement for cross 432 then add in and run again

Removed extra samples and the unknown from the code and going to add cross 432

Removed files: cross_438_2, cross_438_3,unknown_382, control_370,cross_434, 

```{r}
morpho_all <- bind_rows(cross_355, control_370_2, control_371,control_372, control_373, control_374, control_375, control_376, control_378, control_379, PH_385, PH_394, PH_395, PH_400, DO_401, DO_406, DO_409, DO_413, DO_420, cross_432, cross_434_2, cross_437, cross_438_1, DO_491, PH_554 )

dim(morpho_all)
```
select length data only 
```{r}
morpho_length <- morpho_all %>%
  select(X1, Label, Length, ID, treatment)

head(morpho_length)
dim(morpho_length)

```
key to measurement numbers
1 is scale 2-5 filament width 6-9 lamellar length 10-12 lw rep 1 13-15 lw rep 2 16-18 lw rep 3

When pulling columns use select when pulling rows use filter

Subset filament width data for all images 
Only change from here on for each set
```{r}
f_width <- morpho_length %>%
  group_by(Label) %>%
  slice(2:5) %>%
  mutate(avg = mean(Length)) %>%
  select(ID, treatment, avg) %>%
  distinct()
  

head(f_width)
dim(f_width)
```
Graphing filament width

```{r}
ggplot(f_width, aes(x = treatment, y = avg)) + 
  geom_boxplot() +
  ggtitle("Filament Width")
```


Subset lamellar length data for all images 
```{r}
l_length <- morpho_length %>%
  group_by(Label) %>%
  slice(6:9) %>%
  mutate(avg = mean(Length)) %>%
  select(ID, treatment, avg) %>%
  distinct()

head(l_length)
dim(l_length)
```
```{r}
ggplot(l_length, aes(x = treatment, y = avg)) + 
  geom_boxplot() +
  ggtitle("Lamellar Length")
```



